Key Provisioning for the Internet of Things via Light

### 2015-11-01 paper/Zusammenfassung.tex
add results to Zusammenfassung

We implemented a prototype for an Android smartphone and a mote running the Contiki OS.
Contiki is an open source, state-of-the-art operating system for IoT devices\footnote{http://www.contiki-os.org/}.
We also tested techniques to make the transmission reliable.
Besides, we examined how fast the whole transmission could become while maintaining a high chance of correctness.

>>>>

We implemented a prototype for an Android smartphone and a mote running the Contiki OS.
Contiki is an open source, state-of-the-art operating system for IoT devices\footnote{http://www.contiki-os.org/}.
We also tested techniques to make the transmission reliable.
Besides, we examined how fast the whole transmission could become while maintaining a high chance of correctness.
Our results are quite promising as very fast transmission times can be achieved for selected smartphones.
However performance varies a lot between different phone models which may be caused by energy-saving mechanisms.
Future work should target the further automation and reliability improvement of the presented method.
